Moral Foundations of U.S. Political News Organizations

### 2019-03-19 pilot_manuscript.Rmd
trying to figure out NPR

````{r NPR, eval = F, include = F}
library(rvest)
library(RSelenium)
library(beepr)

@@

#create a blank space to put the links
urlslist_final = c()

##loop through the page number at the end until done with ~1000 / 20 = 50
for (i in 1:2){ ##change this to 50

@@

  #get the page source
  webpage <-remDr$getPageSource()

  #pull the links
  headline_data = html_nodes(webpage2,'a')
  attr_data = html_attrs(headline_data)

  #deal with the links
  urlslist = unlist(attr_data)
  urlslist = urlslist[grep("^/201", urlslist)]
  urlslist = unique(urlslist)

  #combine into one list
  urlslist_final = c(urlslist, urlslist_final)

>>>>

````{r NPR_kav, eval = F, include = F}
library(rvest)
library(RSelenium)
library(beepr)

@@

#create a blank space to put the links
urlslist_final = list()

##loop through the page number at the end until done with ~1000 / 20 = 50
for (i in 1:2) { ##change this to 50

@@

  #get the links
  webElems <- remDr$findElements(using = "css", "[href]")
  urlslist_final[[i]] = unlist(sapply(webElems, function(x) {x$getElementAttribute("href")}))
